Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
Conclusions: Adding a few sentences for the TODO note about Tim and Costa.

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage its members to follow suit.

\choinote{Suggestion: insert somewhere a paragraph, say, about the two
facilitators who were actively engaging participants with variously tools,
activities, and reminders}
\end{abstract}

@@

In WSSSPE3, we attempted to take what we learned from WSSSPE1 and WSSSPE2 in how
we can collaboratively build a workshop agenda and turn that into an ongoing
community activity. The success or failure of this effort will only become
apparent over time.

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage its members to follow suit.
\end{abstract}

@@

In WSSSPE3, we attempted to take what we learned from WSSSPE1 and WSSSPE2 in how
we can collaboratively build a workshop agenda and turn that into an ongoing
community activity. For the first time in WSSSPE meetings, two professional
event organizers and facilitators were engaged using funding available to the
WSSSPE3 organizing committe. They assisted the organizing committee members
planning the workshop agenda during the months leading up to the conference.
Throughout the workshop, they actively engaged participants with variously
tools, activities, and reminders. The success or failure of these efforts will
only become apparent over time.
